### 2018-04-09 Manuscript/chapter4.tex
Added transcriptomic review

Following up on these phenotypic findings from our previous study, we now aim to understand the corresponding underlying mechanisms. Transcriptomics is one means to achieve this goal. As it stands, there are only a small number of published experiments examining gene expression patterns related to diet effects (\citealt{alaux2}) and IAPV infection effects (\citealt{galbraith}) in honeybees. As far as we know, there are few to no studies investigating honeybee gene expression patterns specifically related to monofloral diets, and few to no studies investigating gene expression patterns related to the interaction effects of diet in any broad sense and viral innoculation in any broad sense in honeybees.

>>>>

Following up on these phenotypic findings from our previous study, we now aim to understand the corresponding underlying mechanisms by which high quality diets protect bees from virus-induced mortality. For example, it is not known whether the protective effect of good diet is due to direct, specific effects on immune function (resistance), or if it is due to indirect effects of good nutrition on energy availability/vigor (resilience). Transcriptomics is one means to achieve this goal. Transcriptomic analysis can help to identify 1) the genomic scale of transcriptomic response to diet and virus infection, 2) whether these factors interact in an additive or synergistic way on transcriptome function, and 3) the types of pathways affected by diet quality and viral infection. This information, heretofore lacking in the literature, can help us to better understand how good nutrition may be able to serve as a "buffer" against other stressors (\citealt{AdamTothReview}). As it stands, there are only a small number of published experiments examining gene expression patterns related to diet effects (\citealt{alaux2}) and IAPV infection effects (\citealt{galbraith}) in honeybees. As far as we know, there are few to no studies investigating honeybee gene expression patterns specifically related to monofloral diets, and few to no studies investigating gene expression patterns related to the interaction effects of diet in any broad sense and viral innoculation in any broad sense in honeybees.
